---
title: "puberty_cca"
author: "Theresa Cheng"
date: "3/29/2019"
output: html_document
---

```{r setup and load data, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# load packages, install as needed
packages = c("tidyr", "dplyr", "ggplot2", "skimr", "knitr", "PMA", "psych", "candisc", "caret")

package.check <- lapply(packages, FUN = function(x) {
  if (!require(x, character.only = TRUE)) {
    install.packages(x, dependencies = TRUE)
    library(x, character.only = TRUE) }})

puberty_EM <- read.csv("/Volumes/psych-cog/dsnlab/TAG/projects/W1_puberty_cca/puberty_df_EM_imputed1.csv")

# acquire hormone only dataframe 
hormones <- puberty_EM[, c("mean_saliva_EST", "mean_saliva_TEST", "mean_saliva_DHEA","hair_EST_pgug","hair_TEST_pgmg", "hair_DHEA_pgmg")] #

# acquire physical maturation self report variables only
physical_mat <- puberty_EM[, c("pds1_height", "pds2_hair", "pds3_skin", "pds4_breasts",  "pbip1_breasts", "pbip2_pubic_hair")] # "pds6_period",
#physical_mat <- as.data.frame(lapply(physical_mat, factor, ordered = TRUE)) # recode all of these as factors

rm(packages, package.check)
```

```{r inspect univariate descriptive stats, echo = FALSE}

# univariate descriptive statistics
skim(hormones)
skim(physical_mat)
skim(puberty_EM$ageS2)
```

Examining univariate descriptive statistics of our dataset verifies that there is no missing data due to EM imputation at a prior step. Transformed hormone distributions are approximately normal, and we should verify whether the lower and upper limits are within biologically plausible ranges (did not set bounds during imputation). Ignoring the middle column of the PDS data (because its responses have four levels rather than five), the physical maturation data is approximately normal as well. In contrast, the age distribution is fairly flat, verifying that we sampled fairly evenly across the age range.

```{r inspect bivariate descriptive stats, echo = FALSE}

# hormone to hormone
cor_matrix_h <- cor(hormones)
corrplot::corrplot(cor_matrix_h, type = "upper",
         tl.col = "black", tl.srt = 45)

# physical maturation to physical maturation
cor_matrix_pm <- cor(physical_mat, method = "spearman") # ordinal data
corrplot::corrplot(cor_matrix_pm, type = "upper",
         tl.col = "black", tl.srt = 45)

# hormones to physical maturation
cor_matrix_h_pm <- cor(hormones, physical_mat)
corrplot::corrplot(cor_matrix_h_pm, tl.col = "black", tl.srt = 45)
```

Examining correlation matrices suggests that the high correlations between the physical maturation measures (especially those between the PDS items related to hair growth and breast development, along with similar PBIP measures) might problematic in terms of collinearity. Additionally, the fairly low correlations between some of the hair hormone measures (especially the negative correlations with DHEA) may add noise to the model. 

```{r cca functions}
# Modified from Dinga et al., 2018 

select_and_cca_fit <- function(X, Y){
  #select
  correlations <- cor(Y, X, method = "spearman")
  correlations <- apply(correlations, 2, function(x){max(abs(x))})
  corr.threshold <- sort(correlations, decreasing = T)
  selected.X <- correlations >= corr.threshold
  selected.X <- X[,selected.X]
  #cca fit
  cca_model <- candisc::cancor(selected.X, Y)
  #return fitted model containing canonical correlations and wilks lambdas
  return(cca_model)
}

predict.cancor <- function(cancor.obj, X, Y){
  X_pred <- as.matrix(X) %*% cancor.obj$coef$X
  Y_pred <- as.matrix(Y) %*% cancor.obj$coef$Y
  XY_pred <- list(X_pred, Y_pred)
  names(XY_pred) <- c("X_pred", "Y_pred")
  return(XY_pred)
}

cca_cv <- function(hormone_variables, phys_mat_variables, age){
  n_folds <- 10
  folds <- createFolds(as.factor(age), n_folds, list=F)
  results_cancor <- list()
  
  for (fold in 1:n_folds) {
    
    # create training and test set
    train_hormones <- hormone_variables[folds != fold,]
    train_phys_mat <- phys_mat_variables[folds != fold,]
    test_hormones <- hormone_variables[folds == fold,]
    test_phys_mat <- phys_mat_variables[folds == fold,]
   
     # fit on training set
    cancor.fit <- select_and_cca_fit(train_hormones, train_phys_mat)
    
    # predict on test set
    XY_pred_cancor <- predict.cancor(cancor.fit,
                                     test_hormones[,cancor.fit$names$X],
                                     test_phys_mat)
    results_cancor[[fold]] <- diag(cor(XY_pred_cancor[[1]],
    XY_pred_cancor[[2]]))
    
  }
return(do.call(rbind, results_cancor))
}

```

```{r run with candisc functions}

physical_mat_pds <- physical_mat[, c("pds1_height", "pds2_hair", "pds3_skin", "pds4_breasts" )]
physical_mat_pbip <- physical_mat[, c("pds1_height", "pbip2_pubic_hair", "pds3_skin", "pbip1_breasts")]

# run once with pds hair and breast measures
cca_model <- select_and_cca_fit(hormones, physical_mat)

cca_model$cancor

canonical.variates <- predict.cancor(cca_model,
  hormones[,cca_model$names$X],
  physical_mat)

cca_x_loadings <- cor(hormones, canonical.variates$X_pred)
cca_x_loadings

cca_y_loadings <- cor(physical_mat, canonical.variates$Y_pred)
cca_y_loadings

cor_matrix_pm
```

Using all of the data, the canonical loadings of breast development onto the second variate are both positively and negatively associated with breast development. It seems likely that multicollinearity is an issue. We note particularly high correlations between pds2_hair and pbip2_pubic_hair, and pds4_breasts and pbip1_breasts. For now, we take the approach of running everything with PDS only, and then re-running with pbip in order to compare how using difference questionnaires for those two measures impacts the canonical loadings.

```{r}

# run once with pds hair and breast measures
cca_model_pds <- select_and_cca_fit(hormones, physical_mat_pds)

cca_model_pds$cancor

canonical.variates <- predict.cancor(cca_model_pds,
  hormones[,cca_model_pds$names$X],
  physical_mat_pds)

cca_x_loadings_pds <- cor(hormones, canonical.variates$X_pred)
cca_x_loadings_pds
cca_y_loadings_pds <- cor(physical_mat_pds, canonical.variates$Y_pred)
cca_y_loadings_pds

par(mfrow=c(1,2))

plot(canonical.variates$X_pred[,1],
  canonical.variates$Y_pred[,1],
  bty='n',
  xlab='Hormone canonical variate 1',
  ylab='Physical mat pds canonical variate 1')
round(cca_model_pds$cancor[1], 2) # doesn't work, but r = .55

plot(canonical.variates$X_pred[,2],
  canonical.variates$Y_pred[,2],
  bty='n',
  xlab='Hormone canonical variate 2',
  ylab='Physical mat pds canonical variate 2')
round(cca_model_pds$cancor[2], 2) # doesn't work, but r = .35

real_model_pds <- cca_model_pds
real_results_cancor <- real_model_pds$cancor
real_results_wilks_pds <- Wilks(real_model_pds)
real_results_wilks_pds
```

The first canonical variate seems to explain significant variation in the data, but none of the others. Examining both the x and y loadings suggests that this is a general puberty factor. 




```{r cca with pbip hair and breast measures}

# run once with pbip hair and breast measures
cca_model_pbip <- select_and_cca_fit(hormones, physical_mat[, c("pds1_height", "pbip2_pubic_hair", "pds3_skin", "pbip1_breasts" )])

cca_model_pbip$cancor

canonical.variates <- predict.cancor(cca_model_pbip,
  hormones[,cca_model_pbip$names$X],
  physical_mat_pbip)

cca_x_loadings_pbip <- cor(hormones, canonical.variates$X_pred)
cca_x_loadings_pbip
cca_y_loadings_pbip <- cor(physical_mat_pbip, canonical.variates$Y_pred)
cca_y_loadings_pbip
par(mfrow=c(1,2))

plot(canonical.variates$X_pred[,1],
  canonical.variates$Y_pred[,1],
  bty='n',
  xlab='Hormone canonical variate 1',
  ylab='Physical mat pbip canonical variate 1')
round(cca_model_pbip$cancor[1], 2) # doesn't work, but r = .55

plot(canonical.variates$X_pred[,2],
  canonical.variates$Y_pred[,2],
  bty='n',
  xlab='Hormone canonical variate 2',
  ylab='Physical mat pbip canonical variate 2')
round(cca_model_pbip$cancor[2], 2) # doesn't work, but r = .35

real_model <- cca_model_pbip
real_results_cancor <- real_model$cancor
real_results_wilks_pbip <- Wilks(real_model)
```




```{r run cca in pma}

#using PMA package

# use permutations to identify best L1 bound for x and z
perm.out <- CCA.permute(hormones, physical_mat, typex = "standard", typez = "standard", nperms = 100, penaltyxs=seq(.1,1,len=10), penaltyzs=seq(.1,1,len=10))
print(perm.out)
plot(perm.out)

cca_output <- CCA(x = hormones, z = physical_mat, typex = "standard", typez = "standard", penaltyx = .9, penaltyz = .9, K = 3)
# note: in examining the pma package documentation and the linked paper (Tibshirani and Wang), it seems that the "ordered" type doesn't deal with ordinal data, but rather with columns that have some kind of order to them, as in genes on a chromosome as in comparative genomic hybridization data. 

# okay so damn. PMA offers penalized CCA options but no Wilks lambda test. candisc offers the reverse. PMA *DOES* have a permutation test and seems to handle the multicollinearity a bit better, but it only ever shows the FIRST variate. 

```

# next examine CCA with ordinal variables? package homals may be a place to start. but it seems like the next direction may be 